Case for Support

### 2021-11-17 application/trackRecord.tex

The GCNU is an authority in computational neuroscience and
machine learning, while the Sainsbury Wellcome Centre is a world-leading experimental
neuroscience research institute. They share a common building, which facilitates regular interaction and collaboration across various research groups, including the two named PIs in this project, and also collaborate in many joint activities.
%
NeuroGEARS is a spinoff of the SWC and is currently contributing to a major
collaborative research project between the SWC and the GCNU. It developed
Bonsai, a unique ecosystem for experimental control and data acquisition,
and offers courses around the globe instructing students on advanced
experimental control. NeuroGEARS has used Bonsai in numerous research and private experimental projects, and has extensive experience on the
implementation of neuroscience experiments.

>>>>

The GCNU is an authority in computational neuroscience and
machine learning, while the Sainsbury Wellcome Centre is a world-leading experimental
neuroscience research institute. They share a common building, which facilitates regular interaction and collaboration across various research groups, including the two named PIs in this project, and also collaborate in many joint activities.
%
NeuroGEARS is a consulting company started by the creators of Bonsai, a unique ecosystem
for experimental control and data acquisition. It is currently contributing to a major
collaborative research project between the SWC and the GCNU. It continues to develop Bonsai,
and offers courses around the globe instructing students on advanced experimental control.
NeuroGEARS has used Bonsai in numerous research and private experimental projects,
and has extensive experience on the implementation of neuroscience experiments.
